### 2023-03-13 main/chapter_2ljets.tex
add aux cutflows appendix

\begin{table}[tp]
\centering
\begin{tabular}{ccll}
Year & $\ell\ell$ & Trigger & Comment
\\[0.2em]
\hline
2015 & $ee$     & {\footnotesize HLT\_2e12\_lhloose\_L12EM10VH} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_mu18\_mu8noL1} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_mu14} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_mu24} & \\[0.8em]
%
2016 & $ee$     & {\footnotesize HLT\_2e15\_lhvloose\_nod0\_L12EM13VH} & except run 300540 \\
2016 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0} & run 300540, periods D4-- \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & period A \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & from period B \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu20\_mu8noL1} & periods A-D3 \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & periods from D4 \\
2016 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e24\_lhmedium\_nod0\_L1EM20VHI\_mu8noL1}\hspace{-3em} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2017 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & except periods B5--B8 \\
2017 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2018 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & \\
2018 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\
\end{tabular}
\caption[
Detailed trigger specifications
]{
Detailed trigger specifications for the $\twoljets$ analysis in all four
years of Run~2.
These are the dilepton triggers with the weakest available requirements.
Some information can be scraped from the name of each trigger.
Run numbers and periods mentioned in the ``Comment'' column indicate specific
parts of each LHC run, and are chosen on the advice of internal \atlas\
documentation and relate to local operating
conditions~\cite{atlas_twiki_lowest_unprescaled}.
This table is adapted from supporting material for the $\twoljets$ search
paper~\cite{atlas2022searches}.
}
\label{tab:2ljets_trigger_int}
\end{table}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/2ljets_presel_met_logy.png}
\\
\includegraphics[width=0.6\textwidth]{figures/2ljets_presel_met_sig_logy.png}
\caption[
Illustration of how $\metsig$ beats $\met$ in sensitivity to example signal
models
]{
Illustration of how $\metsig$ beats $\met$ in sensitivity to example signal
models; $\met$ is the missing transverse momentum, and $\metsig$ is its
significance as defined in Section~\ref{sec:2ljets_metsig}.
At large $\metsig$, $\ttbar$ and other backgrounds are suppressed, leaving
quite pure \diboson\ backgrounds and greater significance measures.
Signal models with smaller mass-splittings tend to have the bulk of their
events at smaller $\met$.
\\
This selection requires two same-flavour opposite-sign signal leptons with
$\pt^{\ell_2} > 25\,\eV[G]$,
$\mll \in 71\textrm{--}111\,\eV[G]$,
$\mjj \in 60\textrm{--}110\,\eV[G]$,
$\nbtag \leq 1$,
$\met > 100\,\eV[G]$, and
$\metsig > 6$;
these variables are defined in Section~\ref{sec:2ljets_cheatsheet}.
\\
``Significance'' in the lower plot is
$Z_{Bi}$ from~\cite{cousins2008evaluation}, with a $30\%$ uncertainty and
yields taken to the right of a given value.
}
\label{fig:2ljets_presel_met}
\end{figure}

>>>>

\begin{table}[tp]
\centering
\begin{tabular}{ccll}
Year & $\ell\ell$ & Trigger & Comment
\\[0.2em]
\hline
2015 & $ee$     & {\footnotesize HLT\_2e12\_lhloose\_L12EM10VH} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & \\
2015 & $\mu\mu$ & {\footnotesize HLT\_mu18\_mu8noL1} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_mu14} & \\
2015 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_mu24} & \\[0.8em]
%
2016 & $ee$     & {\footnotesize HLT\_2e15\_lhvloose\_nod0\_L12EM13VH} & except run 300540 \\
2016 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0} & run 300540, periods D4-- \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu10} & period A \\
2016 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & from period B \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu20\_mu8noL1} & periods A-D3 \\
2016 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & periods from D4 \\
2016 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e24\_lhmedium\_nod0\_L1EM20VHI\_mu8noL1}\hspace{-3em} & \\
2016 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2017 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & except periods B5--B8 \\
2017 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2017 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2017 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\[0.8em]
%
2018 & $ee$     & {\footnotesize HLT\_2e17\_lhvloose\_nod0\_L12EM15VHI} & \\
2018 & $ee$     & {\footnotesize HLT\_2e24\_lhvloose\_nod0} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_2mu14} & \\
2018 & $\mu\mu$ & {\footnotesize HLT\_mu22\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e17\_lhloose\_nod0\_mu14} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e26\_lhmedium\_nod0\_mu8noL1} & \\
2018 & $e\mu$   & {\footnotesize HLT\_e7\_lhmedium\_nod0\_mu24} & \\
\end{tabular}
\caption[
Detailed trigger specifications
]{%
Detailed trigger specifications for the $\twoljets$ analysis in all four
years of Run~2.
These are the dilepton triggers with the weakest available requirements.
Some information can be scraped from the name of each trigger.
Run numbers and periods mentioned in the ``Comment'' column indicate specific
parts of each LHC run, and are chosen on the advice of internal \atlas\
documentation and relate to local operating
conditions~\cite{atlas_twiki_lowest_unprescaled}.
This table is adapted from supporting material for the $\twoljets$ search
paper~\cite{atlas2022searches}.
}
\label{tab:2ljets_trigger_int}
\end{table}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/2ljets_presel_met_logy.png}
\\
\includegraphics[width=0.6\textwidth]{figures/2ljets_presel_met_sig_logy.png}
\caption[
Illustration of how $\metsig$ beats $\met$ in sensitivity to example signal
models
]{%
Illustration of how $\metsig$ beats $\met$ in sensitivity to example signal
models; $\met$ is the missing transverse momentum, and $\metsig$ is its
significance as defined in Section~\ref{sec:2ljets_metsig}.
At large $\metsig$, $\ttbar$ and other backgrounds are suppressed, leaving
quite pure \diboson\ backgrounds and greater significance measures.
Signal models with smaller mass-splittings tend to have the bulk of their
events at smaller $\met$.
\\
This selection requires two same-flavour opposite-sign signal leptons with
$\pt^{\ell_2} > 25\,\eV[G]$,
$\mll \in 71\textrm{--}111\,\eV[G]$,
$\mjj \in 60\textrm{--}110\,\eV[G]$,
$\nbtag \leq 1$,
$\met > 100\,\eV[G]$, and
$\metsig > 6$;
these variables are defined in Section~\ref{sec:2ljets_cheatsheet}.
\\
``Significance'' in the lower plot is
$Z_{Bi}$ from~\cite{cousins2008evaluation}, with a $30\%$ uncertainty and
yields taken to the right of a given value.
}
\label{fig:2ljets_presel_met}
\end{figure}
